\section{Introduction}~\label{sec:intro}


Boolean satisfiability (SAT) solving is a core tool in computer science with
applications in program
verification~\cite{BillionQueries,sat-hardwareverification,ic3,bmc},
planning~\cite{planning,planningassat}, cryptography~\cite{cryptominisat}, and
mathematics~\cite{chromaticnumber,pythagoreantriples,kellersconjecture,emptyhexagon}.
As its usage expands, so too does the need for more powerful and specialized
solving techniques.



% It is most commonly solved using the conflict-driven clause learning (CDCL)
% framework. This framework explores the state space of possible solutions,
% while learning clauses when it reaches a conflict, to aid future explorations.
One such class of techniques is propagation redundant (\pr) clause
learning~\cite{prclauses}. In this technique, a solver generates and adds
clauses which are satisfiability-preserving; that is, clauses whose conjunction
with the formula is satisfiable if and only if the original formula is
satisfiable. The solver aims to learn clauses that drastically shrink the
potential solution space, such as clauses that break symmetries.

%A classic problem involving symmetries is the pigeonhole problem, which asks if
%it is possible to fit $n+1$ pigeons into $n$ holes with at most one pigeon per
%hole. In this problem, one may learn a clause equivalent to the lemma:
%\emph{pigeon 1 is not in hole 1}. Adding this clause restricts the search space
%for the first pigeon (and thus the problem), but it preserves satisfiability,
%as hole 1 is symmetric with all holes.

% One can ensure that these clauses are satisfiable within the given proof
% system.

% for instance vivification and blocked clause addition. These techinques use
% other facts about the formula to learn clauses which are often useful for
% solving.

The power of this technique is tied to the strength of the underlying proof
system. A more powerful proof system can admit shorter proofs, which can be
found and checked quicker. Most SAT solvers rely on resolution-based proof
systems, which are ineffective for many hard instances. Consider the pigeonhole
principle (PHP), which asks if it is possible to fit $n+1$ pigeons into $n$
holes with at most one pigeon per hole. With a linear number of \pr reasoning
steps, one may learn a \pr clause equivalent to the lemma: \emph{pigeon 1 is not
in hole 1}. Adding this clause restricts the search space for the first pigeon
(and thus the problem), but it preserves satisfiability, as hole 1 is symmetric
with all holes. 

It is difficult to perform similar reasoning compactly with resolution, and in
fact, PHP is known to require exponentially large resolution
proofs~\cite{hakenpigeonhole}. Proof systems
based on \pr clauses, however, have short proofs for such problems, including a
cubic proof (in the number of pigeons) for PHP~\cite{prclauses}. PHP is especially
important as it occurs frequently as a subproblem for many different SAT benchmarks.

The theoretical power of \pr learning comes at a cost, and efficiently learning
useful \pr clauses is a challenge. State-of-the-art techniques such as
Satisfiability Driven Clause Learning (SDCL) rely on calling another SAT solver
to verify that a candidate clause is \pr \cite{sadical}. 
% This is both expensive and difficult to integrate into existing tools. 
Thus, in the worst case, the solver takes exponential time to learn a single \pr
clause. This makes integration into high-performance solvers difficult and
limits their practical impact. To the best of our knowledge, none of the most popular SAT solvers
such as \cadical~\cite{cadical}, \kissat~\cite{kissat},
\cryptoMiniSAT~\cite{cryptominisat}, or \lingeling~\cite{lingeling} support
\pr clause learning in their main branch.
% maybe cite cryptominisat instead of lingeling? todo : check crypto mini sat to
% see if it uses \pr clauses

% todo : should we explain what conditional autarkies are? or go more into depth
% about globally blocked clauses?
In this work, we propose a new, more efficient approach to learn \pr clauses
based on conditional autarkies. Intuitively, a conditional autarky provides a
way to force the value of certain variables given a set of assumptions, e.g., in
PHP if pigeons $3 $ to $ n+1$ are not in hole $1$ or hole $2$ (see \autoref{subfig:pigeonholeclause-c}
for a visual representation), then pigeon $1$
can be placed in hole $1$ and pigeon $2$ can be placed in hole $2$. Kiesl et.
al. proposed an algorithm for finding conditional autarkies in linear
time~\cite{conditionalautarkies}, using them to delete clauses. In our work, we
will use conditional autarkies to construct and add \pr clauses. 
%We make use of an algorithm proposed by Kiesl et. al. for finding a conditional
%autarky given a assignment in linear time. 
%
%Given a assignment to a SAT formula, our method divides the assignment
%into a \emph{conditional} part and an \emph{autarky} part. Using this
%distinction, we can learn a globally blocked clause (a type of \pr clause) in
%linear time.

While conditional autarkies present a means for bridging the theoretical gap in
identifying \pr clauses, the \pr clauses they produce are not immediately useful
in real SAT solving applications. There are two major practical limitations: (1)
larger \pr clauses may not meaningfully constrain the search space, and (2) some
smaller \pr clauses may be trivial and distract the solver. We solve (1) by
introducing a shrinking procedure to extract compact, useful \pr clauses, and
(2) by introducing a number of heuristics for filtering away trivial \pr
clauses. Returning to PHP, instead of the conditional autarky described above
which produces a clause with at least $2n$ literals, it is possible through
shrinking to learn a binary \pr clause either forbidding pigeon $1$ in hole $2$ or
pigeon $2$ in hole $1$.
% todo: would like to say more about what these heuristics are

% Integrating \pr clause learning into a SAT solver is still an active area of
% study

To summarize, we make the following contributions: 

\begin{enumerate} 
    \item We introduce a method for learning \pr clauses in linear time in the
    size of the formula. 
    \item We develop a number of shrinking and filtering heuristics, to learn
    concise and useful \pr clauses.% from conditional autarkies.. 
    \item We implement these techniques in a solver, \tool\footnote{\tool's code
    is available at \url{https://github.com/amarshah10/cautical}.} (a fork of
    the state-of-the-art SAT solver \cadical), and evaluate it on pigeonhole 
    principle benchmarks and a suite of benchmarks from the annual SAT competitions.
\end{enumerate}